%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{ivana}{vantuchová}{softwarový inženýr}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{kontakt}
Přadlácká 920/24c
602 00 Brno
Česká Republika
~
(+420) 774 614 714
~
haraslinova.ivana
@gmail.com
\section{languages}
slovenština | rodný
angličtina | plynulý
italština | plynulý
\section{progarmování}
{\color{red} $\varheartsuit$} C\#, PHP, CSS, HTML
\section{technologie}
ASP.NET, MVC.NET 
MySQL, T-SQL
REST, SOA
Drupal
\section{IDEs}
Visual Studio
PHPStorm
\section{grafika}
Adobe Illustrator
Adobe InDesign
Adobe Photoshop
Adobe Ligtroom
\end{aside}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{profil}
A developer with master degree in information technology and experience with back-end programming from corporate as well as small business environment. 
I worked in on development of SOA application with REST based services. I enriched my theroetical knowledge while writing thesis on REST servicies and thier versioning. I have excellent communication skills and I pay attention to detail. In a small agency I developed websites based on Drupal CMS. I improved analysis skills, discipline and time management as I usually worked from abroad. My professional goal is to become a full stack developer with good technical skill set and theoretical overview.

\section{experience}

\begin{entrylist}
%------------------------------------------------
  \job
  {July 2015 \\ --- \\ now}
  {Proof \& Reason s.r.o.}
  {Brno, Czech Republic}
  {UX focused digital agency}
  {
    \position
    {Freelance software developer}
    {Drupal}
    {Implementation of several projects.
    I was responsible for project analysis, TWIG template implementation and site building according to supplied graphic design.}
  }
%------------------------------------------------
\job
{September 2014 \\ --- \\ June 2015}
{FNZ Ltd. - Czech branch}
{Brno, Czech Republic}
{Provides financial investment platforms to financial institutions}
{
  \position
  {Software developer}
  {C\#, VB, SOA, REST, Visual Studio, Jira}
  {of wealth management web application, my part of service layer designed according to REST service layer development and maintenance for financial investment system.
  I worked in an international team of roughly ten people, cooperating on daily basis with MVC team, core functionality teams.
  }
}
%------------------------------------------------
\job
{August 2014}
{FNZ Ltd. - Czech branch}
{Brno, Czech Republic}
{Provides financial investment platforms to financial institutions}
{
  \position
  {Summer internship}
  {C\#, JavaScript, Razor, MVC, Visual Studio}
  {Development of an internal MVC application.
  In a team of four we developed an employee holiday planner. According to propsed design we created entities, controllers and views.}
}
%------------------------------------------------
\job
{2012 \\ --- \\ 2014}
{various customers}
{}
{}
{
  \position{Freelance graphic designer}
  {Adobe Illustrator, Adobe InDesign, Adobe Photoshop}
  {During my studies I was working on several small graphic projects. Mostly logo design and branding but also book covers, pages design and layouts and mobile application graphic design. My bachelor thesis was on Visual identity for a real customer. I designed logo, promotional items and provided graphic manual.}
}
%------------------------------------------------
\end{entrylist}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2012--2015}
{Master {\normalfont Service Science, Management and Engineering}}
{Masaryk University, Brno}
{\emph{Specialization in project management and SOA.} \\ Thesis in SOA, REST services versioning. I analysed REST services of an existing company and proposed options for their versioning. Main goal was to offer and maintain custom tailored functionality for various customers.}
%------------------------------------------------
\entry
{2009--2012}
{Bachelor {\normalfont Applied Infrmatics}}
{Masaryk University, Brno}
{\emph{General information technology programme, with voluntary specialization in graphic design.} \\ Thesis in Visual identity for an educational project. The thesis covered whole process of creating a logo and unified visual identity for real life customer.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	COMMUNICATION SKILLS SECTION
%----------------------------------------------------------------------------------------

%\section{communication skills}

%\begin{entrylist}
%------------------------------------------------
%\entry
%{2011}
%{Oral Presentation}
%{California Business Conference}
%{Presented the research I conducted for my Masters of Commerce degree.}
%------------------------------------------------
%\entry
%{2010}
%{Poster}
%{Annual Business Conference, Oregon}
%{As part of the course work for BUS320, I created a poster analyzing several local businesses and presented this at a conference.}
%------------------------------------------------
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} web technologies, Drupal, PHP, ASP.Net, SOA \\
\textbf{personal:} books, sports, yoga, travelling, health, photography, design

%----------------------------------------------------------------------------------------
\end{document}
