%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

    \header{marek}{vantuch}{freelance software engineer \& consultant}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

    \begin{aside}
        \section{contact}
        Pradlacka 920/24c
        602 00 Brno
        Czech Republic
        ~
        (+420) 774 614 714
        ~
        marek@vantuch.com
        \section{languages}
        Czech | mother tongue
        English | fluent
        (IELTS Band 8)
        \section{programming}
        {\color{red} $\varheartsuit$} PHP
        JavaScript, SQL
        CSS, HTML
        \section{technologies}
        {\color{red} $\varheartsuit$} Drupal 7, 8, 9, 10
        Symfony, Composer
        PHPUnit, Behat
        CI/CD, Deployer
        Bitbucket, GitLab
        GitHub, Azure Pipelines
        Acquia
        IoC, Git
        \section{metodologies}
        SCRUM, TDD
        SOA
        \section{IDEs}
        PHPStorm
    \end{aside}

    \section{profile}
    I am a Drupal and PHP developer, architect and consultant.
    Over the past years, I have lead development of several e-publishing and e-commerce projects, all of which were deployed on-time and are being used to this day.
    Some of those were built from scratch, some were pre-existing and some were converted from previous versions of Drupal.
    My focus is designing the architecture of the solution as well as the quality, performance and structure of the resulting code.

    % GENERIC
    % Over the last couple of years I have used wide range of programming languages and technologies including a short time of JAVA Android development.
    % I've been working as a freelancer on various .NET and Drupal projects, designing and implementing several REST APIs.
    % I enjoy challenges, learning new technologies and solving problems.

    \bigskip


    \section{experience}
    \begin{entrylist}
        \job
        {present \\ --- \\ 06 / 2025}
        {European Union Agency for Asylum}
        {Valletta, Malta}
        {Agency of the European Union mandated with supporting member states in asylum handling}
        {
            \position
            {Drupal Developer}
            {Drupal, PHP, SQL, PWA, JavaScript, HTML, SASS, CSS, GIT, CI/CD, Azure DevOps}
            {
                Implementation of online forms made to support field workers in various operations.
            }
        }
        \job
        {03 / 2025 \\ --- \\ 09 / 2019}
        {Carrier Fire \& Security}
        {Brussels, Belgium}
        {Fire safety, security, building automation, heating, ventilating and air conditioning systems manufacturer and distributor}
        {
            \position
            {Drupal Architect \& Consultant}
            {Drupal, PHP, SQL, REST, Behat, Azure, JavaScript, Angular, HTML, SASS, CSS, GIT, CI/CD, Bitbucket, Azure DevOps}
            {
                An online B2B sales platform maintenance and implementation project.
            }
        }
        \job
        {08 / 2019 \\ --- \\ 02 / 2019}
        {Český Rozhlas (Czech Radio)}
        {Prague, Czech Republic}
        {Public radio broadcaster of Czech Republic}
        {
            \position
            {Drupal Architect \& Developer}
            {Drupal, PHP, REST, MySQL, HTML, CSS, JavaScript, GIT, CI/CD, Bitbucket, Github}
            {
                A pilot project and implemenation of an online streaming platform based on Drupal 8 CMS. Integration
                with the front-end and implementation of APIs for mobile apps.
            }
        }
    \end{entrylist}

    \begin{entrylist}
        \job
        {06 / 2019 \\ --- \\ 08 / 2014}
        {Proof \& Reason s.r.o.}
        {Brno, Czech Republic}
        {UX focused digital agency}
        {
            \position
            {Drupal Architect, Team lead \& Developer}
            {Drupal, Symfony, PHP, MySQL, JavaScript, AJAX, Grunt, TWIG, HTML, SASS, GIT}
            {
                Cooperated as a freelancer on various projects ranging from e-commerce solutions to publishing platforms, leading a team of up to 5 developers.
            }% \\
        % \emph{Key Successes:}
        % \begin{itemize}
        %   \item Three projects I had been responsible for were deployed on time and in accordance with the client's requirements.
        %   \item Culsulting on other projects in regard of proper and clean 'Drupal' ways of implementation and architecture.
        %   \item Freelance cooperation on a news page for Czech Radio.
        % \end{itemize}
        }
        \job
        {12 / 2018 \\ --- \\ 11 / 2017}
        {Xequals}
        {Wellington, New Zealand}
        {Drupal digital agency}
        {
            \position
            {Drupal Backend Engineer}
            {Drupal, PHP, SQL, JavaScript, REST, GIT}
            {
                On a part time basis, I had helped with maintaining an australian Drupal website. Part of this
            was implementing a custom REST API and improve the structure and stability of the existing solution.
            }
        }
        \job
        {11 / 2017 \\ --- \\ 05 / 2017}
        {MetService}
        {Wellington, New Zealand}
        {New Zealand's meterological service}
        {
            \position
            {Full Stack Software Engineer}
            {Drupal, PHP, SQL, Android, JAVA, JavaScript, SQL, GIT, HTML}
            {
                I cooperated on maintenance and enhancements of one of the New Zealand's busiest websites and it's derivates along with their Android \& IOS apps.
                As a main project, I designed and implemented a prototype of a new public alert system.
            }
        }
        \job
        {04 / 2017 \\ --- \\ 01 / 2017}
        {Český Rozhlas (Czech Radio)}
        {Prague, Czech Republic}
        {Public radio broadcaster of Czech Republic}
        {
            \position
            {Drupal Architect \& Developer}
            {Drupal, PHP, SQL, JavaScript, SQL, REST}
            {
                With a colleague, we have implemented a news portal based on Drupal. Project had specific requirements for
            it's front-office, speed and ease of use for it's users. Part of this was also an API for it's mobile application.
            }% \\
        % \emph{Key Successes:}
        % \begin{itemize}
        %  \item Just in two programmers, we delivered the back-end of site within three months time.
        %  \item Successfully overcome problems with integrating to their current solution.
        % \end{itemize}
        }

        \job
        {06 / 2015 \\ --- \\ 06 / 2014}
        {Oriflame Software s.r.o.}
        {Olomouc, Czech Republic}
        {Software department of a major cosmetics company \emph{Oriflame Sweden}}
        {
            \position
            {Back-End Developer}
            {MVC.NET, C\#, JavaScript, AJAX, NHibernate, IoC, TFS}
            {Back-end development for a custom built e-commerce solution.
            I was part of a team which was implementing a redesigned version of an existing online shop.
            Target was to operate in more than fifty countries on Azure backend with in-memory queries and additional high-performance features.
            Whole solution was built from scratch and I was responsible for designing several of it's parts and implementation of others.}\\
            \position
            {Android Developer}
            {Android, JAVA, GIT}
            {Android part of our project was running behind.
            I was offered to start working on Android app and cooperate on it's development, taking over some parts of the application.}\\
            \position
            {REST Architect \& Developer}
            {ASP.NET Web API, C\#, NHibernate, IOC, GIT}
            {Analysis, design and implementation of a REST API backend for an Android application.
            With another colleague we were responsible for the back-end part of the application and implemented a Web API solution to provide
            accounts and storage for the Android front-end.}% \\
        % \emph{Key Successes:}
        % \begin{itemize}
        %  \item Managed to fluently jump into a running Android project with no previous knowledge of the technology.
        %  \item Implemented several new design features into the MVC application, expanding it to MVVP pattern and therefore
        %  allowed for it to be a bit clearer and simpler.
        % \end{itemize}\medskip
        }
    \end{entrylist}

    \begin{entrylist}
        \job
        {05 / 2014 \\ --- \\ 02 / 2014}
        {NetSuite Czech Republic s.r.o.}
        {Brno, Czech Republic}
        {American company offering cloud based services for managing large businesses}
        {
            \position
            {Software Engineer}
            {JAVA, JavaScript, Oracle SQL, GIT}
            {Working in the team focused on deploying an online project management tool as part of the NetSuite product.
            I had quit after three months for the lack of challenges.}
        }
        \job
        {04 / 2012 \\ --- \\ 02 / 2012}
        {Spark (Vietnam)}
        {Ha Noi, Viet Nam}
        {Social Entrepreneurship Development NGO}
        {
            \position
            {Drupal architect \& developer}
            {Drupal, PHP, JavaScript, HTML, CSS}
            {During an internship, I had designed and implemented a web portal for Spark Social Entrepreneurship Development organization.}
        }
        \job
        {05 / 2013 \\ --- \\ 09 / 2010}
        {FNZ Czechia}
        {Brno, Czech Republic}
        {Provides financial investment platforms to financial institutions}
        {
            \position
            {Project Development Lead}
            {MVC.NET, REST API, C\#, JavaScript, JIRA, SCRUM, Accurev, Project Management}
            {Finished last development stage of an online investment platform and managed it's support during first months after it's
            release to market. Besides managing development team, I provided estimates and contributed to project planning
            while communicating to client side employees.}\\
            \position
            {Team Lead}
            {ASP.NET, C\#, VB.NET, JavaScript, JIRA, Accurev}
            {I was assigned to of smaller projects and lead it's development duriring support phase. I implemented new changes
            into it's codebase along with several improvements to technologies and architecture.}\\
            \position
            {.NET Developer}
            {ASP.NET, MVC.NET, C\#, JavaScript, REST API, Accurev}
            {Worked on many separate projects in multiple technologies in both C\# and VB.NET. I was sent to New Zealand for
            several months long business trip to help local development and transfer some of their skills back to our office.}%\\
        % \emph{Key Successes:}
        % \begin{itemize}
        %  \item Stabilized a previously infamous project and started delivering expected work with team of roughly seven developers.
        %  \item Improved processes and deployements to streamline the development and reduce overhead.
        % \end{itemize}\medskip
        }
    \end{entrylist}

    \pagebreak

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------


    \section{education}

    \begin{entrylist}
        \entry
        {\parbox[t]{2cm}{\centering 2014 \\ --- \\ 2011}}
        {Master {\normalfont Service Science, Management and Engineering}}
        {Masaryk University, Brno}
        {
            \thesis
            {Specialization in project management and SOA.}
            {Thesis in implementation of remote machine connection from HTML5 compatible browser.}
        }
        \entry
        {\parbox[t]{2cm}{\centering 2010}}
        {Erasmus Programme {\normalfont Information Technology}}
        {Yildiz Technical University, Istanbul}
        {Exchange student during a single term.\medskip}
        \entry
        {\parbox[t]{2cm}{\centering 2011 \\ --- \\ 2007}}
        {Bachelor {\normalfont Information Technology}}
        {Brno university of technology, Brno}
        {
            \thesis
            {General information technology programme.}
            {Thesis in natural language morphological tagging.}
        }
    \end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------


    \section{awards}

    \begin{entrylist}
        \entry
        {\parbox[t]{2cm}{\centering 2019}}
        {Drupal CS Awards}
        {Drupal.cz, Czech Republic}
        {Best website built in Drupal CMS.}
        \entry
        {\parbox[t]{2cm}{\centering 2018}}
        {Web TOP 100}
        {WebTop100, Prague, Czech Republic}
        {Shared second place for the Newton COLLEGE project (by the Proof \& Reason agency).}
        \entry
        {\parbox[t]{2cm}{\centering 2017}}
        {Web TOP 100}
        {WebTop100, Prague, Czech Republic}
        {Third place for the Skrivanek project (by the Proof \& Reason agency).}
        \entry
        {\parbox[t]{2cm}{\centering 2010}}
        {VIP2 Contest Winner}
        {CZ.NIC, Prague, Czech Republic}
        {Won the price for finishing one of suggested projects.}
    \end{entrylist}

    \section{interests}

    \textbf{professional:} Linux, Drupal, SCRUM, time management, web technologies \\
    \textbf{personal:} travelling, photography, reading, cycling, motorcycling

\end{document}
