%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.0 (5/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{marek}{vantuch}{freelance software engineer}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
41 Mitchell street
Brooklyn
6021 Wellington
~
(+64) 224 750 571
~
marek@vantuch.com
\section{languages}
Czech | mother tongue
English | fluent
(IELTS Band 8)
\section{programming}
{\color{red} $\varheartsuit$} C\#, JavaScript
PHP, JAVA
CSS, HTML
SQL
\section{technologies}
{\color{red} $\varheartsuit$} MVC.NET {\color{red} $\varheartsuit$} Drupal
Web API, IoC
XUnit, PHPUnit
Git
\section{metodologies}
SCRUM, TDD
SOA
\section{IDEs}
Visual Studio + ReSharper
PHPStorm
\end{aside}

%----------------------------------------------------------------------------------------
%	PROFILE SECTION
%----------------------------------------------------------------------------------------
\section{profile}
I am a Full-Stack developer with mostly web development experience.
Over the last couple of years I have used wide range of languages and technologies including short term of Android JAVA development.
I mostly work with MVC and try to use the best features of each of the languages and technologies in each project I work on.
I enjoy challenges, learning new technologies and interesting ways of solving issues.
I don't consider myself to be a great finisher and sometimes it takes me longer than necessary to polish every bit of the solution.

I don't mind doing a bit of management and I enjoyed my role as a development lead.
After leading a team for a while, I try to provide exact estimates and then do it ideally sooner.
\bigskip
%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}
\begin{entrylist}
  \job
  {08 / 2014 \\ --- \\ 03 / 2017}
  {Proof \& Reason s.r.o.}
  {Brno, Czech Republic}
  {UX focused digital agency}
  {
    \position
    {Drupal Architect \& Developer}
    {Drupal, Symfony, PHP, JavaScript, AJAX, Grunt, TWIG, HTML, SASS}
    {
      Cooperated as a freelancer on various projects. Most of the projects I was the sole developer and architect.
      Projects were ranging from one site e-commerce solutions to sizeable solutions for some of Czech companies.
      Largest project was an administration for German newspaper house which is still being developed today and will
      be eventually re-sold as a product. I was mostly responsible for custom implementations and alterations to
      core Drupal behaviour along with advanced JavaScript and AJAX implementations.
    }\\
    \emph{Key Successes:}
    \begin{itemize}
      \item Three projects I had been responsible for were deployed on time and in accordance with the client's requirements.
      \item Culsulting on other projects in regard of proper and clean 'Drupal' ways of implementation and architecture.
    \end{itemize}
  }
\end{entrylist}

\begin{entrylist}
  \job
  {06 / 2014 \\ --- \\ 06 / 2015}
  {Oriflame Software s.r.o.}
  {Olomouc, Czech Republic}
  {Software department of a major cosmetics company \emph{Oriflame Sweden}}
  {
    \position
    {Back-End Developer}
    {MVC.NET, C\#, JavaScript, AJAX, NHibernate, IoC, TFS}
    {Back-end development for a custom built e-commerce solution. I was part of a team which was implementing
    a redesigned version of currently running online shop. Target was to run an application in more than fifty countries
    on an Azure backend with in-memory queries and additional high-performance features. Whole solution was built and
    designed from scratch and I was responsible for designing several of it's parts and implementation of others.}\\
    \position
    {Android Developer}
    {Android, JAVA, GIT}
    {Android part of our project was running behind, so I learned Android and cooperated on it's development, taking
     over few parts of the application.}\\
    \position
    {REST Architect \& Developer}
    {ASP.NET Web API, C\#, NHibernate, IOC, GIT}
    {Analysis, design and implementation of a REST API backend for an Android application. With another colleague
    we were responsible for the back-end part of the application and implemented a Web API solution to provide
    accounts and storage for the Android front-end.}\\
    \emph{Key Successes:}
    \begin{itemize}
      \item Managed to fluently jump into a running Android project with no previous knowledge of the framework.
      \item Implemented several new design features into the MVC application, expanding it to MVVP pattern and therefore
      allowed for it to be a bit clearer and simpler.
    \end{itemize}\medskip
  }
  \job
  {02 / 2014 \\ --- \\ 05 / 2014}
  {NetSuite Czech Republic s.r.o.}
  {Brno, Czech Republic}
  {American company offering cloud based services for managing large businesses}
  {
    \position
    {Software Engineer}
    {JAVA, JavaScript, Oracle SQL, GIT}
    {Working in the team focused on deploying an online project management tool as part of the NetSuite product.
    I had quit after three months for lack of challenge and joy.}
  }
  \job
  {02 / 2012 \\ --- \\ 04 / 2012}
  {Spark (Vietnam)}
  {Ha Noi, Viet Nam}
  {Social Entrepreneurship Development NGO}
  {
    \position
    {Drupal architect \& developer}
    {Drupal, PHP, JavaScript, HTML, CSS}
    {During an internship, I had designed and implemented a web portal for Spark Social Entrepreneurship Development
    organization.}
  }
\end{entrylist}

\begin{entrylist}
  \job
  {09 / 2010 \\ --- \\ 05 / 2013}
  {FNZ Czechia}
  {Brno, Czech Republic}
  {Provides financial investment platforms to financial institutions}
  {
    \position
    {Project Development Lead}
    {MVC.NET, REST API, C\#, JavaScript, JIRA, SCRUM, Accurev, Project Management}
    {Finished development stage of an online investment platform and managed it's support during first months after it's
    release to market. Besides managing development team, I provided estimates and contributed to project planning
    while communicating to client side employees.}\\
    \position
    {Team Lead}
    {ASP.NET, C\#, VB.NET, JavaScript, JIRA, Accurev}
    {I was assigned to of smaller projects and lead it's development duriring support phase. I implemented new changes
    into it's codebase along with several improvements to technologies and architecture.}\\
    \position
    {.NET Developer}
    {ASP.NET, MVC.NET, C\#, JavaScript, REST API, Accurev}
    {Worked on many separate projects in multiple technologies in both C\# and VB.NET. I was sent to New Zealand for
    several months long business trip to help local development and transfer some of their skills back to our office.}\\
    \emph{Key Successes:}
    \begin{itemize}
      \item Stabilized a previously infamous project and started delivering expected work with team of roughly seven developers.
      \item Improved processes and deployements to streamline the development and reduce overhead.
    \end{itemize}\medskip
  }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\section{education}

\begin{entrylist}
  \entry
  {\parbox[t]{2cm}{\centering 2011 \\ --- \\ 2014}}
  {Master {\normalfont Service Science, Management and Engineering}}
  {Masaryk University, Brno}
  {
    \thesis
    {Specialization in project management and SOA.}
    {Thesis in implementation of remote machine connection from HTML5 compatible browser.}
  }
  \entry
  {\parbox[t]{2cm}{\centering 2010}}
  {Erasmus Programme {\normalfont Information Technology}}
  {Yildiz Technical University, Istanbul}
  {Exchange student during a single term.\medskip}
  \entry
  {\parbox[t]{2cm}{\centering 2007 \\ --- \\ 2011}}
  {Bachelor {\normalfont Information Technology}}
  {Brno university of technology, Brno}
  {
    \thesis
    {General information technology programme.}
    {Thesis in natural language morphological tagging.}
  }
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{\parbox[t]{2cm}{\centering 2010}}
{VIP2 Contest Winner}
{CZ.NIC, Prague, Czech Republic}
{Won the price for finishing one of suggested projects.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} Linux, Drupal, SCRUM, time management, web technologies \\
\textbf{personal:} travelling, sports, photography, reading, cycling, motorcycling

\end{document}
